\begin{thebibliography}{9}
\addcontentsline{toc}{section}{References} % Add an entry for this in the table of contents

\bibitem{FracBrownMotion}
	Mandelbrot, B. \& Van Ness, J. (1968) \\ 
	``\textit{Fractional Brownian Motions, Fractional Noises and Applications}'' \\
	SIAM Review, Vol. 10, No. 4, pp. 422-437
	
\bibitem{ShadowMapping}
	Williams, L. (1978) \\ 
	``\textit{Casting Curved Shadows on Curved Surfaces}'' \\
	Computer Graphics Lab, New York Institute of Technology, Old Westbury, New York 11568 
	
\bibitem{ImprovedShadowMapping}
	Microsoft, Dev Center (2013) \\ 
	``\textit{Common Techniques to Improve Shadow Depth Maps}'' \\
	\href{http://msdn.microsoft.com/en-us/library/windows/desktop/ee416324(v=vs.85).aspx}{http://msdn.microsoft.com/en-us/library/windows/desktop/ee416324(v=vs.85).aspx}
	
\bibitem{CascadeShadowMapping}
	Microsoft, Dev Center (2013) \\ 
	``\textit{Cascaded Shadow Maps}'' \\
	\href{http://msdn.microsoft.com/en-us/library/windows/desktop/ee416307(v=vs.85).aspx}{http://msdn.microsoft.com/en-us/library/windows/desktop/ee416307(v=vs.85).aspx}
	
\bibitem{LSPShadowMapping}
	Wimmer, M., Scherzer, D. \& Purgathofer, W. (2004) \\ 
	``\textit{Light Space Perspective Shadow Maps}'' \\
	Vienna University of Technology, Austria \\

	
\bibitem{citekey}
\bibitem{citekey}

\bibitem{Gardel}
	Gardel, A., Bravo, I., Jimenez, P., Lazaro, J.L. \& Torquemada, A.\\
	``\textit{Statistical Background Models with Shadow Detection for Video Based Tracking},''\\ Intelligent Signal Processing, 2007. WISP 2007. IEEE International Symposium on?? Page: 1-6.
	
\bibitem{Zivkovic}
	Zivkovic, Z. \& Heijden, F.\\
	``\textit{Efficient Adaptive Density Estimation per Image Pixel for the Task of Background Subtraction},''\\
	Pattern recognition letters, Vol. 27, No. 7. (2006), pp. 773-780.

\bibitem{MOTA}
	Bernardin, K. \& Stiefelhagen, R (2008)\\
	``\textit{Evaluating Multiple Object Tracking Performance: The CLEAR MOT Metrics},''\\
	Interactive Systems Lab, Institut für Theoretische Informatik,\\
	Universität Karlsruhe, 76131 Karlsruhe, Germany
	
\bibitem{CAVIAR}
	``\textit{CAVIAR: Context Aware Vision using Image-based Active Recognition},''\\
	EC Funded CAVIAR project/IST 2001 37540\\
	http://homepages.inf.ed.ac.uk/rbf/CAVIAR/
	
\bibitem{StereoBM}
	Hirschmüller, H (2008)\\
	``\textit{Stereo Processing by Semiglobal Matching and Mutual Information},''\\
	IEEE Transactions on Pattern Analysis and Machine Intelligence, Volume 30(2)
	pp. 328-341.
	
\bibitem{OpenCV}
	OpenCV \textit{Open source computer vision}\\
	http://docs.opencv.org/\\
	Accessed on 2013-12-13\\
	

%\bibitem{somePaper}
%	Q. Lastname,
%	``Some article title,''
%	\emph{Some scientific journal},
%	vol.~1337, no.~1337,
%	pp.~666--1337,
%	month.~1337.

\end{thebibliography}